An Embedding Framework for Consistent Polyhedral Surrogates

### 2021-09-27 poly-embed-journal/poly-embed-journal.tex
Pass on Sec 6, 7, 8, appendix A

\jessie{Attempted brief overview}
In \S~\ref{sec:poly-loss-embed}, we discussed the connection between embeddings and polyhedral losses, and a natural next question is to understand if polyhedral losses are necessary to embed a discrete loss --- the answer is negative.
Here, we further study the structure of embeddings, showing instead that discrete losses must be embedded by a function with polyhedral Bayes risk, which have finite minimum representative sets.
For intuition, we show in \S~\ref{subsec:match-BR} that the embedding condition simplifies to matching Bayes risks (Proposition~\ref{prop:embed-bayes-risks}).
Since surrogates with polyhedral Bayes risk have finite minimum representative sets, we introduce and study the notion of a trimmed loss, and connect this to tight embeddings and non-redundancy from property elicitation.

\raf{Add somewhere: initially explored by~\citet{wang2020weston} under the name \emph{embedding cardinality} }
\jessie{Feels like we should mention that earlier, when minimum representative set is introduced? -- mentioned it right under the definition of representative set}

@@

While we have focused on polyhedral losses thus far, it turns out that many of our results about embeddings extend to losses with polyhedral Bayes risks.
(We say a concave function is polyhedral if its negation is a polyhedral convex function.)
To see that this is a weaker condition, recall that Theorem~\ref{thm:poly-embeds-discrete} constructs a finite representative set $\Sc$ for any polyhedral loss $L$, and thus $\risk{L} = \risk{L|_\Sc}$ by Lemma~\ref{lem:loss-restrict}, which is polyhedral.
The condition is strictly weaker, in that the Bayes risk may be polyhedral even if the loss itself is not.
For example, a modified hinge loss $L(r)_y = \max(r^2-1,1-ry)$ as shown in Figure~\ref{fig:modified-hinge}, which matches hinge loss on the interval $[-1,1]$ but is smooth outside the interval $[-2,2]$, still embeds twice 0-1 loss.

@@

We now present our main structural result in Lemma~\ref{lem:X}, which will lay the foundation for the rest of this section.
Lemma~\ref{lem:X} observes that a (minimizable) loss $L$ with polyhedral Bayes risk have finite representative sets, and derives equivalent conditions on the level sets of the property elicited by $L$ and tight embeddings.
\raf{TODO: Brief description of the result}\jessie{Attempted}

@@

	For the reverse implication, assume $\risk{L} = \risk{\ell}$, which are polyhedral functions as $\ell$ is discrete.
  From Lemma~\ref{lem:X}(\ref{item:X-min-V}), we have some set $\V\subseteq\reals^\Y_+$ and minimum representative sets $\R^* \subseteq \R$ and $\U^* \subseteq \U$, for $\ell$ and $L$ respectively, such that $\ell(\R^*) = \V = L(\U^*)$.\jessiet{This is a different $\Sc$ than the first paragraph, right? The first $\Sc$ is representative for $\ell$.}\raft{They are both quantified separately, so not linked; are you saying it's confusing to use $\Sc$ here though because its role is slightly different?}\jessiet{Yes... attempting to clarify.}
  As $\R^*$ and $\U^*$ are miniumum, they cannot repeat loss vectors, and thus $|\R^*|=|\ell(\R^*)|$ and $|L(\U^*)|=|\U^*|$.
  We conclude that $\R^*$ and $\U^*$ are both in bijection with $\V$.
  The map $\varphi :\R^* \to \reals^d$, given by $\varphi(r) = u \in \U^*$ where $\ell(r) = L(u)$, is therefore well-defined.
  Condition (i) of an embedding is immediate.
  From Proposition~\ref{prop:representative-embeds-restriction}, $\ell$ embeds $\ell|_{\R^*}$ and $L$ embeds $L|_{\U^*}$, both via the identity embedding.
  Using condition (ii) from both embeddings, for all $p\in\simplex$ and $r\in\R^*$, we have
  \begin{equation*}
    r \in \gamma(p) \iff r \in \prop{\ell|_{\R^*}}(p) \iff \varphi(r) \in \prop{L|_{\U^*}}(p)
    \iff \varphi(r) \in \prop{L}(p)~,
  \end{equation*}
  giving condition (ii).
\end{proof}

@@

\begin{proposition}\label{prop:embed-iff-trims-equal}
  Let $L:\reals^d\to\reals^\Y_+$ have a finite representative set, and let $\ell:\R\to\reals^\Y_+$ be a discrete loss.
  Then $L$ embeds $\ell$ if and only if $\trimcover(L) = \trimcover(\ell)$.
  Furthermore, $L$ tightly embeds $\ell$ if and only if $\ell$ is injective and $\trimcover(L) = \ell(\R)$.
\end{proposition}
\begin{proof}
  \raft{This is sort of a ``clever'' proof, probably not in a good way.  Something that used Lemma X more directly would probably be better than using Bayes risk matching.  But if correct I think it's not bad. \jessie{It's a little subtle in parts, but checks out to me.}}
  As $L$ has a finite representative set, it is minimizable.
  Proposition~\ref{prop:embed-bayes-risks} gives $L$ embeds $\ell$ if and only if $\risk L = \risk \ell$.
  If $\risk L = \risk \ell$, Lemma~\ref{lem:X}(\ref{item:X-min-V}) gives $\trim(L) = \trim(\ell)$.
  For the converse, suppose $\trim(L) = \trim(\ell) =: \V$.
  Define the discrete loss $\ell_\trim : \V \to \V, v\mapsto v$.
  Then $\ell_\trim$ is injective and $\ell_\trim(\V) = \V$, so from Lemma~\ref{lem:X}(\ref{item:X-tight-embed}), both $L$ and $\ell$ tightly embed $\ell_\trim$.
  We conclude $\risk L = \risk{\ell_\trim} = \risk \ell$ from Proposition~\ref{prop:embed-bayes-risks}.
  The second statement also follows directly from Lemma~\ref{lem:X}(\ref{item:X-tight-embed}).
\end{proof}

@@

\begin{definition}[Non-redundancy]\label{def:nonredundant}
  A loss $L : \R \to \reals^\Y_+$ eliciting $\Gamma:\simplex \toto \R$ is \emph{redundant} if there are reports $r, r' \in \R$ such that $\Gamma_r \subseteq \Gamma_{r'}$, and \emph{non-redundant} otherwise.
\end{definition}

@@

  Now suppose $L|_{\R'}$ is non-redundant.
  As $\R'$ is a representative set, Lemma~\ref{lem:X}(\ref{item:X-rep-contain-min}) gives some minimum representative set $\Sc \subseteq \R'$.
  Suppose we had some $r \in \R' \setminus \Sc$.
  Now Lemma~\ref{lem:X}(\ref{item:X-min-Theta},\ref{item:X-redundant}) gives some $s\in\Sc$ such that $\Gamma_r \subseteq \Gamma_s$, which contradicts $L|_{\R'}$ being non-redundant.
  We conclude $\Sc=\R'$, meaning $\R'$ is a minimum representative set.
\end{proof}

@@

  For the reverse inclusion, let $r\in\R\setminus\red(\Gamma)$.
  Let $\Sc$ again be a minimum representative set for $L$.
  From Lemma~\ref{lem:X}(\ref{item:X-min-Theta},\ref{item:X-redundant}), we have some $s\in\Sc$ such that $\Gamma_r \subseteq \Gamma_s$.
  By definition of $\red(L)$, we conclude $\Gamma_r = \Gamma_s$.
  Now take $\Sc' = (\Sc \setminus \{s\}) \cup \{r\}$, that is, the same set of reports with $r$ replacing $s$.
  We have $\{\Gamma_s \mid s\in\Sc\} = \{\Gamma_{s'} \mid s'\in\Sc'\}$, and thus $\Sc'$ is minimum representative for $L$ by Lemma~\ref{lem:X}(\ref{item:X-min-Theta}).
  As $r\in\Sc'$, we have $r \in \R'$ and we are done.
\end{proof}

@@

We conclude this section with a similar structural result about the properties elicited or embedded by another property.
We say a property $\Gamma:\simplex\toto\reals^d$ embeds a finite property $\gamma:\simplex\toto\R$ if condition (ii) of Definition~\ref{def:loss-embed} holds.
In other words, $\Gamma$ embeds $\gamma$ if we have some representative set $\Sc\subseteq\R$ for $\gamma$ and embedding $\varphi:\Sc\to\reals^d$ such that for all $s\in\Sc$ we have $\gamma_s = \Gamma_{\varphi(s)}$.
% The definitions of representative sets and embeddings naturally extend to properties.
% We say a set 
% As we define embeddings from one loss to another, one can define embeddings from one property to another, where essentially condition (i) is relaxed; see \S~\ref{app:embed-props} for a precise definition.
Furthermore, when working with properties, it is more natural to define ``trim'' to remove any level sets which are strictly redundant.
Precisely, we define $\trimred(\Gamma) := \{\Gamma_r \mid r \in \R\setminus\red(\Gamma)\}$.
%\R \textrm{ s.t. } \neg\exists r'\in\R,r'\neq r,\, \Gamma_r \subsetneq \Gamma_{r'}\}~.\]

With these definitions, we now state a structural result for embeddable properties, and the properties that embed them.
First, if $\Gamma$ embeds $\gamma$ and $\gamma$ is non-redundant, the level sets of $\Gamma$ must all be redundant relative to $\gamma$.
In other words, $\Gamma$ is exactly the property $\gamma$ \jessie{up to relabelling reports}, just with other reports filling in the gaps between the embedded reports of $\gamma$.
When working with convex losses, these extra reports often arise as the convex hull of the embedded reports.
In this sense, we can regard embedding as only a slight departure from direct elicitation: if a loss $L$ elicits $\Gamma$ which embeds $\gamma$, we can think of $L$ as essentially eliciting $\gamma$ itself.
Finally, we have an important converse: if $\Gamma$ has finitely many full-dimensional level sets, or if $\trimred(\Gamma)$ is finite, then $\Gamma$ must embed some finite elicitable property with those same level sets.

@@

\jessie{Adding in small motivation of Prop 6}
This allows us to think about the structure of properties elicited by losses with finite representative sets in the following equivalent ways through $\trimred(\Gamma)$.

\begin{proposition}\label{prop:embed-trim}
  Let $\Gamma:\simplex\toto\reals^d$ be an elicitable property.\jessiet{$\reals^d$ vs $\R$?}\raft{Can't recall why we needed $\reals^d$.  Probably don't... in any case, can't use $\R$ since that clashes with $\gamma$.}
  The following are equivalent:
  \begin{enumerate}\setlength{\itemsep}{0pt}
  \item $\Gamma$ embeds a elicitable finite property $\gamma:\simplex \toto \R$.
  \item $\trimred(\Gamma)$ is a finite set.%, and $\cup\,\trimred(\Gamma) = \simplex$.
  % \\ $\hat\Gamma := \trimred(\Gamma)$ is a finite property, and $\cup\,\hat\Gamma) = \simplex$.
  \item There is a finite minimum representative set $\U$ for $\Gamma$.
  \item There is a finite set of full-dimensional level sets $\hat\Theta$ of $\Gamma$, and $\cup\,\hat\Theta = \simplex$.
  \end{enumerate}
  % \raft{I see why you wanted this addition here, but (a) it's clear from the def of embedding, and (b) we don't have varphi defined.  So let's leave it out.}
  Moreover, when any of the above hold, $\trimred(\gamma) = \trimred(\Gamma) = \{\Gamma_u \mid u\in\U\} = \hat\Theta$.
\end{proposition}

\begin{proof}
  Let $L$ be a fixed loss eliciting $\Gamma$, so that in particular $\risk L$ is fixed.
  By definition of elicits, $L$ is minimizable.
  In each case, we will show that $\risk L$ is polyhedral, and thus Lemma~\ref{lem:X} will give us the set $\Theta$ of full-dimensional level sets of $\Gamma$, uniquely determined by $\risk L$.
  We will prove $1 \Rightarrow 2 \Rightarrow 3 \Rightarrow 4 \Rightarrow 1$, and in each case show that the relevant set of level sets is equal to $\Theta$, giving the result.

  Case 1:
  Let $\Sc$ be the representative set for $\gamma$ and $\varphi:\Sc\to\reals^d$ the embedding.
  Since $\Sc$ is finite, $\varphi(\Sc)$ is a finite representative set for $\Gamma$ (and $L$).
  Corollary~\ref{cor:trim-prop-red} now gives $\trimred(\Gamma) = \Theta$, which is finite, showing Case 2.

  Case 2:
  \raf{Somehow I had like 5 typos in here which made it impossible to follow.  Hopefully better now!}
  If $\trimred(\Gamma)$ is finite, then in particular we have a finite set of reports $\Sc \subseteq \reals^d\setminus\red(\Gamma)$ such that $\trimred(\Gamma) = \{\Gamma_s \mid s\in\Sc\}$.
  As $\Gamma$ is elicitable, $\reals^d$ is representative for $\Gamma$.
  By definition of $\trimred$, we have $\simplex = \cup_{r\in\reals^d} \Gamma_r = \cup \trimred(\Gamma) = \cup_{s\in\Sc} \Gamma_s$, and therefore $\Sc$ is representative for $\Gamma$ and for $L$.\jessiet{I'm a bit confused by this- how do we get $\cup_{\reals^d}\Gamma_r \subseteq \cup \trimred(\Gamma)$?}\raft{Each level set on the left is contained in one on the right}
  From Lemma~\ref{lem:X}(\ref{item:X-rep-contain-min}), we have some minimum representative set $\U\subseteq\Sc$ for $L$ and $\Gamma$, showing Case 3.
  Moreover, Lemma~\ref{lem:X}(\ref{item:X-min-Theta},\ref{item:X-full-dim}) gives $\{\Gamma_u \mid u\in\U\} = \Theta$.
  \jessie{My understanding: we have a representative set $\R$, but don't know if it's finite.  However, we have $\Sc$ that [nonredundantly] generates trim, which is finite by assumption, and need to show that's representative.  Once we have $\Sc$ a finite representative set, we can apply Lemma X to say it also contains a finite \emph{minimum} rep set.}

  Case 3:
  Let $\U$ be a finite minimum representative set.
  Lemma~\ref{lem:X}(\ref{item:X-min-Theta},\ref{item:X-full-dim}) once again gives $\{\Gamma_u \mid u\in\U\} = \Theta$.
  We simply let $\hat\Theta = \Theta$, giving Case 4 as $\U$ is representative.

  Case 4:
  Let $\Sc\subseteq\R$ such that $\{\Gamma_s \mid s\in\Sc\} = \hat \Theta$.
  Then $\Sc$ is representative for $\Gamma$ and $L$, as $\cup\hat\Theta = \simplex$.
  Lemma~\ref{lem:loss-restrict} now states that $L$ embeds $L|_\Sc$, so $\Gamma$ embeds $\gamma := \Gamma|_\Sc$, giving Case 1.
  Finally, Corollary~\ref{cor:trim-prop-red} gives $\trimred(\gamma) = \Theta$.
  %
  % Letting $\Theta_\ell$ be the full-dimensional level sets of $\gamma$, Corollary~\ref{cor:trim-prop-red} also gives $\trimred(\gamma) = \Theta'$.
  % From Lemma~\ref{lem:X}(\ref{item:X-rep-contain-min}), we have some minimum representative set $\U\subseteq\U'$ for $L$ and $\Gamma$.
  % We have $\{\gamma_r\mid \varphi(r)\in\U\} = \{\Gamma_u \mid u\in\U\} = \Theta$ by Lemma~\ref{lem:X}(\ref{item:X-min-Theta}) and definition of embedding.
  % As $\Theta$ is a set of full-dimensional level sets of $\gamma$, we must have $\Theta \subseteq \Theta_\ell$.
  % But as $\cup \Theta = \simplex$, we must have $\Theta = \Theta_\ell$, as otherwise there exists $s\in\Sc$ with $\gamma_s \in \Theta_\ell \setminus \Theta$ and thus $\Sc \setminus \{s\}$ would still be representative.
  %
  % 
  % It remains to show $\trimred(\gamma) = \Theta$.
  % Moreover, $\Theta$ is exactly the full-dimensional level sets of $\Gamma$ by Lemma~\ref{lem:X}(\ref{item:X-full-dim}).
  % 
  % From Lemma~\ref{lem:X}(\ref{item:X-min-Theta},\ref{item:X-full-dim}) there exists some set of level sets $\Theta'$ which are the full-dimensional level sets of $\gamma$ and there exists a minimum representative set $\Sc\subseteq\R$ with $\{\gamma_s\mid s\in\Sc\} = \Theta'$.
  % Finally, Lemma~\ref{lem:X}(\ref{item:X-redundant}) gives $\trimred(\gamma) = \Theta$.
\end{proof}

\btw{JOURNAL: cool to point out that when $L$ is polyhedral, $\prop{L}$ has a finite range (this result) and so does its (multivalued map) inverse (trim result)!}

@@

\begin{definition}[Refines]
	Let $\Gamma:\simplex \toto \R$ and $\Gamma':\simplex\toto \R'$.
	Then $\Gamma$ \emph{refines} $\Gamma'$ if for all $r \in \R$, there exists $r' \in \R'$ such that $\Gamma_{r} \subseteq \Gamma'_{r'}$.
\end{definition}
Equivalently, $\Gamma$ refines $\Gamma'$ if there is some ``link'' function $\psi:\R\to\R'$ such that $r\in\Gamma(p) \implies f(r) \in \Gamma'(p)$ for all $p\in\simplex$.
We will use the fact that refinement is transitive: if $\Gamma_1$ refines $\Gamma_2$ and $\Gamma_2$ refines $\Gamma_3$, then $\Gamma_1$ refines $\Gamma_3$.

@@

It is straightforward to verify that consistency, and therefore calibration, implies indirect elicitation\raft{Add cites}.
Indirect elicitation may appear much weaker than calibration, since in particular it does not depend on the loss except through the property it elicits.
Surprisingly, for polyhedral surrogates, we show the converse: indirect elicitation implies calibration, and therefore consistency.

@@

\begin{proof}[Proof of Theorem \ref{thm:eps-thick-calibrated}]
  The two claims are Theorems \ref{thm:small-eps-thick} and \ref{thm:app-eps-thick-sep}.
\end{proof}

\section{Omitted Proofs}\label{app:omitted-proofs}

>>>>

\jessie{Attempted brief overview}
In \S~\ref{sec:poly-loss-embed}, we discussed the connection between embeddings and polyhedral losses; a natural next question is to understand if polyhedral losses are necessary to embed a discrete loss --- the answer is negative.
Here, we further study the structure of embeddings, showing instead that discrete losses must be embedded by a function with polyhedral Bayes risk, which have finite minimum representative sets.
For intuition, we show in \S~\ref{subsec:match-BR} that the embedding condition simplifies to matching Bayes risks (Proposition~\ref{prop:embed-bayes-risks}).
Since surrogates with polyhedral Bayes risk have finite minimum representative sets (Lemma~\ref{lem:X}), we introduce and study the notion of a trimmed loss studying loss values at minimum representative sets, and connect this to both tight embeddings and non-redundancy from property elicitation.

\raf{Add somewhere: initially explored by~\citet{wang2020weston} under the name \emph{embedding cardinality} }
\jessie{mentioned it right under the definition of representative set way earlier}

@@

While we have focused on polyhedral losses thus far, it turns out that many of our results about embeddings extend to losses with polyhedral Bayes risks.
(We say a concave function is polyhedral if its negation is a polyhedral convex function.)
To see that this is a weaker condition, recall that Theorem~\ref{thm:poly-embeds-discrete} constructs a finite representative set $\Sc$ for any polyhedral loss $L$, and thus $\risk{L} = \risk{L|_\Sc}$ by Lemma~\ref{lem:loss-restrict}, which is polyhedral.
The condition of polyhedral Bayes risk is strictly weaker than polyhedral surrogates, in that the Bayes risk may be polyhedral even if the loss itself is not.
For example, a modified hinge loss $L(r)_y = \max(r^2-1,1-ry)$ as shown in Figure~\ref{fig:modified-hinge}, which matches hinge loss on the interval $[-1,1]$ but is smooth outside the interval $[-2,2]$, still embeds twice 0-1 loss.

@@

We now present our main structural result in Lemma~\ref{lem:X}, which will lay the foundation for the rest of this section.
Lemma~\ref{lem:X} observes that (minimizable) losses $L$ with polyhedral Bayes risk have finite representative sets, and derives equivalent conditions on the level sets of the property elicited by $L$ and tight embeddings.
%\raf{TODO: Brief description of the result}\jessie{Attempted}

@@

	For the reverse implication, assume $\risk{L} = \risk{\ell}$, which are polyhedral functions as $\ell$ is discrete.
  From Lemma~\ref{lem:X}(\ref{item:X-min-V}), we have some set $\V\subseteq\reals^\Y_+$ and minimum representative sets $\R^* \subseteq \R$ and $\U^* \subseteq \U$, for $\ell$ and $L$ respectively, such that $\ell(\R^*) = \V = L(\U^*)$.
  %\jessiet{This is a different $\Sc$ than the first paragraph, right? The first $\Sc$ is representative for $\ell$.}\raft{They are both quantified separately, so not linked; are you saying it's confusing to use $\Sc$ here though because its role is slightly different?}\jessiet{Yes... attempting to clarify.}
  As $\R^*$ and $\U^*$ are miniumum, they cannot repeat loss vectors, and thus $|\R^*|=|\ell(\R^*)|$ and $|L(\U^*)|=|\U^*|$.
  We conclude that $\R^*$ and $\U^*$ are both in bijection with $\V$.
  The map $\varphi :\R^* \to \reals^d$, given by $\varphi(r) = u \in \U^*$ where $\ell(r) = L(u)$, is therefore well-defined.
  Condition (i) of an embedding is immediate.
  From Proposition~\ref{prop:representative-embeds-restriction}, $\ell$ embeds $\ell|_{\R^*}$ and $L$ embeds $L|_{\U^*}$, both via the identity embedding.
  Using condition (ii) from both embeddings, for all $p\in\simplex$ and $r\in\R^*$, we have
  \begin{equation*}
    r \in \gamma(p) \iff r \in \prop{\ell|_{\R^*}}(p) \iff \varphi(r) \in \prop{L|_{\U^*}}(p)
    \iff \varphi(r) \in \prop{L}(p)~,
  \end{equation*}
  giving condition (ii).
\end{proof}

@@

\begin{proposition}\label{prop:embed-iff-trims-equal}
  Let $L:\reals^d\to\reals^\Y_+$ have a finite representative set, and let $\ell:\R\to\reals^\Y_+$ be a discrete loss.
  Then $L$ embeds $\ell$ if and only if $\trimcover(L) = \trimcover(\ell)$.
  Furthermore, $L$ tightly embeds $\ell$ if and only if $\ell$ is injective and $\trimcover(L) = \ell(\R)$.
\end{proposition}
\begin{proof}
  \raft{This is sort of a ``clever'' proof, probably not in a good way.  Something that used Lemma X more directly would probably be better than using Bayes risk matching.  But if correct I think it's not bad. \jessie{It's a little subtle in parts, but checks out to me.  Feel free to \# burn}}
  As $L$ has a finite representative set, it is minimizable.
  Proposition~\ref{prop:embed-bayes-risks} gives $L$ embeds $\ell$ if and only if $\risk L = \risk \ell$.
  If $\risk L = \risk \ell$, Lemma~\ref{lem:X}(\ref{item:X-min-V}) gives $\trim(L) = \trim(\ell)$.
  For the converse, suppose $\trim(L) = \trim(\ell) =: \V$.
  Define the discrete loss $\ell_\trim : \V \to \V, v\mapsto v$.
  Then $\ell_\trim$ is injective and $\ell_\trim(\V) = \V$, so from Lemma~\ref{lem:X}(\ref{item:X-tight-embed}), both $L$ and $\ell$ tightly embed $\ell_\trim$.
  We conclude $\risk L = \risk{\ell_\trim} = \risk \ell$ from Proposition~\ref{prop:embed-bayes-risks}.
  The second statement also follows directly from Lemma~\ref{lem:X}(\ref{item:X-tight-embed}).
\end{proof}

@@

\begin{definition}[Non-redundancy]\label{def:nonredundant}
  A loss $L : \R \to \reals^\Y_+$ eliciting $\Gamma:\simplex \toto \R$ is \emph{redundant} if there are reports $r, r' \in \R$ with $r \neq r'$ such that $\Gamma_r \subseteq \Gamma_{r'}$, and \emph{non-redundant} otherwise.
\end{definition}

@@

  Now suppose $L|_{\R'}$ is non-redundant.
  As $\R'$ is a representative set, Lemma~\ref{lem:X}(\ref{item:X-rep-contain-min}) gives some minimum representative set $\Sc \subseteq \R'$.
  Suppose we had some $r \in \R' \setminus \Sc$.
  Now Lemma~\ref{lem:X}(\ref{item:X-min-Theta},\ref{item:X-redundant}) gives some $s\in\Sc$ such that $\Gamma_r \subseteq \Gamma_s$, which contradicts $L|_{\R'}$ being non-redundant.
  We conclude $L(\Sc)=L(\R')$, meaning $\R'$ is a minimum representative set.
\end{proof}

@@

  For the reverse inclusion, let $r\in\R\setminus\red(\Gamma)$.
  Let $\Sc$ again be a minimum representative set for $L$.
  From Lemma~\ref{lem:X}(\ref{item:X-min-Theta},\ref{item:X-redundant}), we have some $s\in\Sc$ such that $\Gamma_r \subseteq \Gamma_s$.
  By definition of $\red(L)$, we conclude $\Gamma_r = \Gamma_s$.
  Now take $\Sc' = (\Sc \setminus \{s\}) \cup \{r\}$, that is, the same set of reports with $r$ replacing $s$.
  We have $\{\Gamma_s \mid s\in\Sc\} = \{\Gamma_{s'} \mid s'\in\Sc'\}$, and thus $\Sc'$ is a minimum representative for $L$ by Lemma~\ref{lem:X}(\ref{item:X-min-Theta}).
  As $r\in\Sc'$, we have $r \in \R'$ and we are done.
\end{proof}

@@

We conclude this section with a similar structural result about the properties embedded by another property.
We say a property $\Gamma:\simplex\toto\reals^d$ embeds a finite property $\gamma:\simplex\toto\R$ if condition (ii) of Definition~\ref{def:loss-embed} holds.
In other words, $\Gamma$ embeds $\gamma$ if we have some representative set $\Sc\subseteq\R$ for $\gamma$ and embedding $\varphi:\Sc\to\reals^d$ such that for all $s\in\Sc$ we have $\gamma_s = \Gamma_{\varphi(s)}$.
% The definitions of representative sets and embeddings naturally extend to properties.
% We say a set 
% As we define embeddings from one loss to another, one can define embeddings from one property to another, where essentially condition (i) is relaxed; see \S~\ref{app:embed-props} for a precise definition.
Furthermore, when working with properties, it is more natural to define ``trim'' to remove any level sets which are strictly redundant.
Precisely, we define $\trimred(\Gamma) := \{\Gamma_r \mid r \in \R\setminus\red(\Gamma)\}$.
%\R \textrm{ s.t. } \neg\exists r'\in\R,r'\neq r,\, \Gamma_r \subsetneq \Gamma_{r'}\}~.\]

With these definitions, we now state a structural result for embeddable properties, and the properties that embed them.
First, if $\Gamma$ embeds $\gamma$ and $\gamma$ is non-redundant, the level sets of $\Gamma$ must all be redundant relative to $\gamma$.
In other words, $\Gamma$ is exactly the property $\gamma$ up to relabelling reports, just with other reports filling in the gaps between the embedded reports of $\gamma$.
When working with convex losses, these extra reports often arise in the convex hull of the embedded reports.
In this sense, we can regard embedding as only a slight departure from direct elicitation: if a loss $L$ elicits $\Gamma$ which embeds $\gamma$, we can almost think of $L$ as essentially eliciting $\gamma$ itself.
Finally, we have an important converse: if $\Gamma$ has finitely many full-dimensional level sets, or if $\trimred(\Gamma)$ is finite, then $\Gamma$ must embed some finite elicitable property with those same level sets.

@@

%\jessie{Adding in small motivation of Prop 6}
This allows us to think about the structure of properties elicited by losses with finite representative sets in the following equivalent ways through $\trimred(\Gamma)$.

\begin{proposition}\label{prop:embed-trim}
  Let $\Gamma:\simplex\toto\reals^d$ be an elicitable property.
  %\jessiet{$\reals^d$ vs $\R$?}\raft{Can't recall why we needed $\reals^d$.  Probably don't... in any case, can't use $\R$ since that clashes with $\gamma$.}
  The following are equivalent:
  \begin{enumerate}\setlength{\itemsep}{0pt}
  \item $\Gamma$ embeds a elicitable finite property $\gamma:\simplex \toto \R$.
  \item $\trimred(\Gamma)$ is a finite set.%, and $\cup\,\trimred(\Gamma) = \simplex$.
  % \\ $\hat\Gamma := \trimred(\Gamma)$ is a finite property, and $\cup\,\hat\Gamma) = \simplex$.
  \item There is a finite minimum representative set $\U$ for $\Gamma$.
  \item There is a finite set of full-dimensional level sets $\hat\Theta$ of $\Gamma$, and $\cup\,\hat\Theta = \simplex$.
  \end{enumerate}
  % \raft{I see why you wanted this addition here, but (a) it's clear from the def of embedding, and (b) we don't have varphi defined.  So let's leave it out.}
  Moreover, when any of the above hold, $\trimred(\gamma) = \trimred(\Gamma) = \{\Gamma_u \mid u\in\U\} = \hat\Theta$.
\end{proposition}

\begin{proof}
  Let $L$ be a fixed loss eliciting $\Gamma$, so that in particular $\risk L$ is fixed.
  By definition of elicitable properties, $L$ is minimizable.
  In each case, we will show that $\risk L$ is polyhedral, and thus Lemma~\ref{lem:X} will give us the set $\Theta$ of full-dimensional level sets of $\Gamma$, uniquely determined by $\risk L$.
  We will prove $1 \Rightarrow 2 \Rightarrow 3 \Rightarrow 4 \Rightarrow 1$, and in each case show that the relevant set of level sets is equal to $\Theta$, giving the result.

  $1 \Rightarrow 2$:
  Let $\Sc$ be the representative set for $\gamma$ and $\varphi:\Sc\to\reals^d$ the embedding.
  Since $\Sc$ is finite, $\varphi(\Sc)$ is a finite representative set for $\Gamma$ (and $L$).
  Corollary~\ref{cor:trim-prop-red} now gives $\trimred(\Gamma) = \Theta$, which is finite, showing Case 2.

  $2 \Rightarrow 3$:
  If $\trimred(\Gamma)$ is finite, then in particular we have a finite set of reports $\Sc \subseteq \reals^d\setminus\red(\Gamma)$ such that $\trimred(\Gamma) = \{\Gamma_s \mid s\in\Sc\}$.
  As $\Gamma$ is elicitable, $\reals^d$ is representative for $\Gamma$.
  By definition of $\trimred$, we have $\simplex = \cup_{r\in\reals^d} \Gamma_r = \cup \trimred(\Gamma) = \cup_{s\in\Sc} \Gamma_s$, and therefore $\Sc$ is representative for $\Gamma$ and for $L$.
  %\jessiet{I'm a bit confused by this- how do we get $\cup_{\reals^d}\Gamma_r \subseteq \cup \trimred(\Gamma)$?}\raft{Each level set on the left is contained in one on the right}
  From Lemma~\ref{lem:X}(\ref{item:X-rep-contain-min}), we have some minimum representative set $\U\subseteq\Sc$ for $L$ and $\Gamma$, implying statement 3.
  Moreover, Lemma~\ref{lem:X}(\ref{item:X-min-Theta},\ref{item:X-full-dim}) gives $\{\Gamma_u \mid u\in\U\} = \Theta$.
  %\jessie{My understanding: we have a representative set $\R$, but don't know if it's finite.  However, we have $\Sc$ that [nonredundantly] generates trim, which is finite by assumption, and need to show that's representative.  Once we have $\Sc$ a finite representative set, we can apply Lemma X to say it also contains a finite \emph{minimum} rep set.}

  $3 \Rightarrow 4$:
  Let $\U$ be a finite minimum representative set.
  Lemma~\ref{lem:X}(\ref{item:X-min-Theta},\ref{item:X-full-dim}) once again gives $\{\Gamma_u \mid u\in\U\} = \Theta$.
  We simply let $\hat\Theta = \Theta$, giving statement 4 as $\U$ is representative.

  $4 \Rightarrow 1$:
  Let $\Sc\subseteq\R$ such that $\{\Gamma_s \mid s\in\Sc\} = \hat \Theta$.
  Then $\Sc$ is representative for $\Gamma$ and $L$, as $\cup\hat\Theta = \simplex$.
  Lemma~\ref{lem:loss-restrict} now states that $L$ embeds $L|_\Sc$, so $\Gamma$ embeds $\gamma := \Gamma|_\Sc$, giving Case 1.
  Finally, Corollary~\ref{cor:trim-prop-red} gives $\trimred(\gamma) = \Theta$.
  %
  % Letting $\Theta_\ell$ be the full-dimensional level sets of $\gamma$, Corollary~\ref{cor:trim-prop-red} also gives $\trimred(\gamma) = \Theta'$.
  % From Lemma~\ref{lem:X}(\ref{item:X-rep-contain-min}), we have some minimum representative set $\U\subseteq\U'$ for $L$ and $\Gamma$.
  % We have $\{\gamma_r\mid \varphi(r)\in\U\} = \{\Gamma_u \mid u\in\U\} = \Theta$ by Lemma~\ref{lem:X}(\ref{item:X-min-Theta}) and definition of embedding.
  % As $\Theta$ is a set of full-dimensional level sets of $\gamma$, we must have $\Theta \subseteq \Theta_\ell$.
  % But as $\cup \Theta = \simplex$, we must have $\Theta = \Theta_\ell$, as otherwise there exists $s\in\Sc$ with $\gamma_s \in \Theta_\ell \setminus \Theta$ and thus $\Sc \setminus \{s\}$ would still be representative.
  %
  % 
  % It remains to show $\trimred(\gamma) = \Theta$.
  % Moreover, $\Theta$ is exactly the full-dimensional level sets of $\Gamma$ by Lemma~\ref{lem:X}(\ref{item:X-full-dim}).
  % 
  % From Lemma~\ref{lem:X}(\ref{item:X-min-Theta},\ref{item:X-full-dim}) there exists some set of level sets $\Theta'$ which are the full-dimensional level sets of $\gamma$ and there exists a minimum representative set $\Sc\subseteq\R$ with $\{\gamma_s\mid s\in\Sc\} = \Theta'$.
  % Finally, Lemma~\ref{lem:X}(\ref{item:X-redundant}) gives $\trimred(\gamma) = \Theta$.
\end{proof}

\btw{JOURNAL: cool to point out that when $L$ is polyhedral, $\prop{L}$ has a finite range (this result) and so does its (multivalued map) inverse (trim result)! \jessie{Think this is a bit outdated.  at least pre lemma X.  Feel free to burn}}

@@

\begin{definition}[Refines]
	Let $\Gamma:\simplex \toto \R$ and $\Gamma':\simplex\toto \R'$.
	Then $\Gamma$ \emph{refines} $\Gamma'$ if for all $r \in \R$, there exists $r' \in \R'$ such that $\Gamma_{r} \subseteq \Gamma'_{r'}$.
\end{definition}
Equivalently, $\Gamma$ refines $\Gamma'$ if there is some ``link'' function $\psi:\R\to\R'$ such that $r\in\Gamma(p) \implies \psi(r) \in \Gamma'(p)$ for all $p\in\simplex$.
We will use the fact that refinement is transitive: if $\Gamma_1$ refines $\Gamma_2$ and $\Gamma_2$ refines $\Gamma_3$, then $\Gamma_1$ refines $\Gamma_3$.

@@

It is straightforward to verify that consistency, and therefore calibration, implies indirect elicitation~\citep{finocchiaro2021unifying,gyorfi2002distribution,fan1998efficient}\raft{Add cites \jessie{Any more?}}.
Indirect elicitation may appear much weaker than calibration, since in particular it does not depend on the loss except through the property it elicits.
Surprisingly, for polyhedral surrogates, we show the converse: indirect elicitation implies calibration, and therefore consistency.

@@

\begin{proof}[Proof of Theorem \ref{thm:link-main}]
  The two claims are Theorems \ref{thm:small-eps-thick} and \ref{thm:app-eps-thick-sep}.
\end{proof}

%\section{Omitted Proofs}\label{app:omitted-proofs}
